\textsf{Are frontier models superhuman chemists?}

### 2024-03-17 src/tex/acronymns.tex
start using showyourwork
update paper
rebuild
start note about tiny benchmarks
feat: add acronyms, fix credits bug, update pipeline
added safety description
fix issues with acronyms

\newacronym{llm}{LLM}{large language model}
\newacronym{ml}{ML}{machine learning}
\newacronym{agi}{AGI}{artificial general intelligence}
\newacronym{api}{API}{application programming interface}
\newacronym{mcq}{MCQ}{multiple-choice question}

>>>>

\newacronym{llm}{LLM}{large language model}
\newacronym{ml}{ML}{machine learning}
\newacronym{agi}{AGI}{artificial general intelligence}
\newacronym{api}{API}{application programming interface}
\newacronym{mcq}{MCQ}{multiple-choice question}
\newacronym{rest}{REST}{Representational State Transfer}
\newacronym{orm}{ORM}{object relational mapping}
\newacronym{dai}{DAI}{daily allowed intake}
\newacronym{ghs}{GHS}{Globally Harmonized System of Classification and Labelling of Chemicals}
\newacronym{who}{WHO}{World Health Organization}
\newacronym{nmr}{NMR}{nuclear magnetic resonance}
\newacronym{helm}{HELM}{Holistic Evaluation of Language Models}
\newacronym{smiles}{SMILES}{Simplified Molecular Input Line-Entry System}
\newacronym{pca}{PCA}{principal component analysis}
\newacronym{iupac}{IUPAC}{International Union of Pure and Applied Chemistry}

### 2024-03-17 src/tex/ms.tex
fix issues with acronyms

\subparagraph{International Chemical Olympiad (\gls{ICHO})}
\variable{output/question_count_per_dir/json_file_counts_icho.txt} questions are based on various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova.

@@

\subparagraph{Chemical safety} 
This category comprises a total of \variable{output/question_count_per_dir/json_file_counts_safety.txt} questions, including semi-programmatically created questions covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \cite{pubchem} (see below for details). 
Additionally, it explores crucial topics like materials' compatibility (\variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} questions) and chemical compatibility (\variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} questions), essential for understanding the hazardous impact of mixing certain materials and chemicals. 
Furthermore, it includes inquiries about the Federal/State Working Group on Chemical Safety (BLAC), consisting of \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} questions. 
These questions are based on the question bank used for the \enquote{Sachkundeprüfung} (expertise examination) according to \§ 11 of the \enquote{Chemikalien-Verbotsverordnung} (Chemical Prohibition Ordinance).
Moreover, this category addresses questions lab safety and topics such as pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. 
The chemical safety category stands out as one of the primary focus areas within the \chembench corpus.

\subparagraph{\gls{NMR} spectroscopy}
Questions are based on images shared via the Twitter account \url{https://twitter.com/NMRspectroscopy}, focusing choosing appropriate \gls{nmr} experiments.

>>>>

\subparagraph{International Chemical Olympiad}
\variable{output/question_count_per_dir/json_file_counts_icho.txt} questions are based on various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova.

@@

\subparagraph{Chemical safety} 
This category comprises a total of \variable{output/question_count_per_dir/json_file_counts_safety.txt} questions, including semi-programmatically created questions covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \cite{pubchem} (see below for details). 
Additionally, it explores crucial topics like materials' compatibility (\variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} questions) and chemical compatibility (\variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} questions), essential for understanding the hazardous impact of mixing certain materials and chemicals. 
Furthermore, it includes inquiries about the Federal/State Working Group on Chemical Safety (BLAC), consisting of \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} questions. 
These questions are based on the question bank used for the \enquote{Sachkundeprüfung} (expertise examination) according to §11 of the \enquote{Chemikalien-Verbotsverordnung} (Chemical Prohibition Ordinance).
Moreover, this category addresses questions lab safety and topics such as pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. 
The chemical safety category stands out as one of the primary focus areas within the \chembench corpus.

\subparagraph{NMR spectroscopy}
Questions are based on images shared via the Twitter account \url{https://twitter.com/NMRspectroscopy}, focusing choosing appropriate \gls{nmr} experiments.
